A note on $\K$ of Kac---Moody groups over a field

### 2017-08-16 paper.tex
Improved wording

Notice that the total numbers of odd and even columns of $d$ are the same as the corresponding numbers for $A$ and $\widetilde{A}$.
In the simplest cases this allows one to immediately compute $\K(A, F)$ by only knowing SNF of $\widetilde{A}$.
\begin{example}
Consider hyperbolic GCM \textnumero~156 from~\cite[p.~19]{MW}.
 Set $A = \left(\begin{smallmatrix}
 2& 0& 0& -1\\
 0& 2& 0& -1\\
 0& 0& 2& -1\\
 -2& -2& -2& 2\end{smallmatrix}\right)$.
Clearly, $A$ has three even columns and one odd column. 
The Smith normal form of $\widetilde{A}$ is $d=\mathrm{diag}(1,2,2,0)$.
Notice that a diagonal coefficient of $d$ can be odd only if the corresponding column is odd.
Thus, we get that $p_d(1)=odd$, $p_d(i)=even$ for $i>1$, hence we compute $\K(A, F)$ as $\Kmw(F)/I \oplus \Kmw(F)/I \oplus \Kmw(F)$,
 which agrees with~\cite{MW}.
\end{example}

@@

\begin{example}
To produce a counterexample, start with GCM 
 $A = \left(\begin{smallmatrix}
 2& -1& -2\\
-3& 2& -4\\
-4& -2& 2\end{smallmatrix}\right)$
  and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$:
\[\widetilde{A} = \left(\begin{smallmatrix}
-3& 1& 0 \\
-4& 0& 2 \\
 0& -2& 4
\end{smallmatrix} \right) = \left(\begin{smallmatrix}
 1& 0& 0\\
 0& 1& 0\\
-2& 2& 1\end{smallmatrix}\right) \cdot \mathrm{diag}(1,2,2) \cdot \left(\begin{smallmatrix}
-3& 1& 0\\
-2& 0& 1\\
 1& 0& 0 \end{smallmatrix}\right) = p \cdot d \cdot q.\]
Looking at the last column of $q$ we get that $1$st and $3$rd columns of $d$ are odd while $2$nd one is even,
 hence $\K(A, F) \cong \Kmw/I \oplus \K(F)/2\K(F)$.

Now set $s:= t_{32}(1)$, $t:= t_{32}(-1) \in \SL(3, \ZZ)$ and consider the decomposition 
$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
Now application of Westaway's criterion to the matrix $sq$ incorrectly determines the parity of the third column of $t^{-1}ds^{-1}=d$ to be even rather than odd.
\end{example}

>>>>

Notice that the total numbers of odd and even columns of $d$ are the same as the corresponding numbers for $A$ and $\widetilde{A}$.
In many cases this allows one to immediately compute $\K(A, F)$ only knowing SNF of $\widetilde{A}$.
\begin{example}
Consider hyperbolic GCM \textnumero~156 from~\cite[p.~19]{MW}.
 Set $A = \left(\begin{smallmatrix}
 2& 0& 0& -1\\
 0& 2& 0& -1\\
 0& 0& 2& -1\\
 -2& -2& -2& 2\end{smallmatrix}\right)$.
Clearly, $A$ has three even columns and one odd column. 
The Smith normal form of $\widetilde{A}$ is $d=\mathrm{diag}(1,2,2,0)$.
Notice that a diagonal coefficient of $d$ can be odd only if the corresponding column is odd.
Thus, we get that $p_d(1)=odd$, $p_d(i)=even$ for $i>1$, and we compute $\K(A, F)$ as $\Kmw(F)/I \oplus \Kmw(F)/I \oplus \Kmw(F)$,
 which agrees with~\cite{MW}.
\end{example}

@@

\begin{example}
To produce a counterexample, start with GCM 
 $A = \left(\begin{smallmatrix}
 2& -1& -2\\
-3& 2& -4\\
-4& -2& 2\end{smallmatrix}\right)$
  and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$:
\[\widetilde{A} = \left(\begin{smallmatrix}
-3& 1& 0 \\
-4& 0& 2 \\
 0& -2& 4
\end{smallmatrix} \right) = \left(\begin{smallmatrix}
 1& 0& 0\\
 0& 1& 0\\
-2& 2& 1\end{smallmatrix}\right) \cdot \mathrm{diag}(1,2,2) \cdot \left(\begin{smallmatrix}
-3& 1& 0\\
-2& 0& 1\\
 1& 0& 0 \end{smallmatrix}\right) = p \cdot d \cdot q.\]
Looking at the last column of $q$ we get that $1$st and $3$rd columns of $d$ are odd while $2$nd one is even,
 hence $\K(A, F) \cong \Kmw(F)/I \oplus \K(F)/2\K(F)$.

Now set $s:= t_{32}(1)$, $t:= t_{32}(-1) \in \SL(3, \ZZ)$ and consider the decomposition 
$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
Now the application of Westaway's criterion to the matrix $sq$ incorrectly gives that the parity of the third column of $t^{-1}ds^{-1}=d$ is even rather than odd
 and, thus, gives another $\Kmw(F)/I$ summand instead of $\K(F)/2\K(F)$.
\end{example}
